% Chapter Template

\chapter{Management Process} % Main chapter title

\label{Part6Chapter4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Part \ref{Part6} \nameref{Part6} Chapter \ref{Part6Chapter4}. \emph{\nameref{Part6Chapter4}}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Project Estimates}

As this project requires no funding we have no costs. Attached to this document you will find a project progress document which includes a GANTT chart which was made prior to the execution stage of this project.

We estimated that the project would begin from the 17th of March, 2014 and end on the 27th of May, 2014.

We have split the project into many phases which have the following estimated durations:
\begin{itemize}
	\item [Initial Project Evaluation] 4 days
	\item [Planning] 15 days
	\item [Execution] 39 days
	\begin{itemize}
		\item [Set up development environment] 3 days
		\item [Iteration 1.1 - Website Construction] 8 days
		\item [Iteration 2.1 - Import Data] 12 days
		\item [Iteration 1.2 - User Management System] 10 days
		\item [Iteration 2.3 - Data Manipulation] 13 days
		\item [Iteration 2.4 - Data Visualisation] 14 days
	\end{itemize}
	\item [Evaluation] 7 days
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Project Plan}

%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 1
%----------------------------------------------------------------------------------------

\subsection{Phase Plan}

The project consisted of four phases being:

\begin{itemize}
	\item Initial Project Evaluation
	\item Planning
	\item Execution
	\item Evaluation
\end{itemize}

\subsubsection{Initial Project Evaluation}

The Initial Project Evaluation consisted of doing some initial research into what we were required to develop for our client. 

Tasks in this phase included:
\begin{itemize}
	\item Identifying Stakeholders
	\item Gathering Requirements
	\item Identifying Resources
	\item Determining External Dependencies
	\item Determining Team Roles
\end{itemize}

\subsubsection{Planning}

The Planning phase consisted of some early development where we began preparing for execution of the project. 

Tasks in this phase included:
\begin{itemize}
	\item Risk Management
	\item Software Requirements Specification
	\item Milestones Document
	\item Project Progress Reports
	\item Feasibility Study
	\item Code of Conduct
	\item Detailed Project Plan
	\item Objectives
	\item Archive Map
	\item Visual Data Document
\end{itemize}

\subsubsection{Execution}

The Execution phase is the largest of all phases which contained all iterations which will be shown in more detail below.

Tasks in this phase included:
\begin{itemize}
	\item Set Up Development Environment
	\item Iterations (shown later)
\end{itemize}

\subsubsection{Evaluation}

The Evaluation phase is when we look back at what we have completed on the project over the last few weeks assess how we went whilst providing relevant documentation

Tasks in this phase included:
\begin{itemize}
	\item Business Cases
	\item Product Objectives and Sub-Objectives
	\item Risk Analysis and Measures
	\item Effort Estimation
	\item Final Software Requirements Specification
	\item Architecture Design
	\item Details of the testing phase
	\item User Manual
	\item Group Meeting Records
	\item Member Contributions 
\end{itemize}



%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 2
%----------------------------------------------------------------------------------------

\subsection{Iteration Objectives}

The objective to having our iterations within the Execution phase was to divide the content of work amongst different team members while still keeping them to a similar time schedule (for example, iterations would be expected to finish at the same date so that those team members can then work together on another iteration together).

%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 3
%----------------------------------------------------------------------------------------

\subsection{Releases}

There is one release planned for the system (Optimus). This is the Monday the 26th of May.

%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 4
%----------------------------------------------------------------------------------------

\subsection{Project Schedule}

Refer to Part 3 for the project (Objectives)

%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 5
%----------------------------------------------------------------------------------------

\subsection{Project Resources}

\begin{itemize}
	\item Server
	\item Gitgub 
	\item Web Server
	\item Mail Server
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 2 SUBSECTION 5 SUBSUBSECTION 3
%----------------------------------------------------------------------------------------

\subsubsection{Training Plan}

For the users of the system, a user manual will be implemneted in order to ease their transition from

	Users: User Manual, Dev Team: Lynda.com, StackOverflow, Google

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Iteration Plan}

Our execution phawe consisted of five iterations:
\begin{itemize}
	\item Iteration 1.1 - Website Construction
	\item Iteration 2.1 - Import Data 
	\item Iteration 1.2 - User Management System 
	\item Iteration 2.3 - Data Manipulation 
	\item Iteration 2.4 - Data Visualisation 
\end{itemize}

Those iterations of group 1.0 were completed by Peter whilst those of group 2.0 were completed by the rest of the group. Once we reached Iteration 2.4 the two groups had merged in order to link up the systems that had been developed.

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Project Monitoring and Control}

%----------------------------------------------------------------------------------------
%	SECTION 4 SUBSECTION 1
%----------------------------------------------------------------------------------------

\subsection{Requirements Management Plan}

Refer to Part \ref{Part7} : \nameref{Part7}

%----------------------------------------------------------------------------------------
%	SECTION 4 SUBSECTION 2
%----------------------------------------------------------------------------------------

\subsection{Schedule Control Plan}

Refer to attached diagram

%----------------------------------------------------------------------------------------
%	SECTION 4 SUBSECTION 4
%----------------------------------------------------------------------------------------

\subsection{Quality Control Plan}

Refer to the testing section/architecture design

%----------------------------------------------------------------------------------------
%	SECTION 4 SUBSECTION 5
%----------------------------------------------------------------------------------------

\subsection{Reporting Plan}

Our process in reporting to the client consisted of weekly meetings. This has proved to be a productive exercise as requirements are added and changed regularly. If we were unable to keep up with client meetings there may be a change in requirements which we would be unprepared to act for.

In the risks document there are details on how we would react in the case that there were any issues with reporting to the client or requirements changing. Please refer to that document for more information.

%----------------------------------------------------------------------------------------
%	SECTION 4 SUBSECTION 6
%----------------------------------------------------------------------------------------

\subsection{Measurement Plan}

The development team will report to the client during the specified meeting times on tuesday from 1330-1530 between weeks 3 and 11 of autumn session with the exception of mid-session break. During the meeting, the client will be illicited for further requirements, current progress will be shown in the progress report.

%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------

\section{Risk Management}

	Refere to Part \ref{Part4}:\nameref{Part4}
%---------------------------------------------------------------------------