% Chapter Template

\chapter{Project Overview} % Main chapter title

\label{Part6Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Part \ref{Part6} \nameref{Part6} Chapter \ref{Part6Chapter2}. \emph{\nameref{Part6Chapter2}}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Project Purpose}

The purpose of project Optimus is to provide an online dashboard system which will allow you to access your own personal profile showing your involvement in the Python development community. It enables you to see through simple,aesthetically pleasing graphs and visualisations data which has been tailored to your experience. Just from registering an account on the system you will be able to view data summaries and statistics with ease in a modern interface.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Project Scope}

The scope of project Optimus is mostly the Python development community as it is their information which is being allowed to be shared around the world for registered users and other developers to see. This gives a simple way of showing data trends from the past and finding useful information in a different way.

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Project Objectives}

The objectives of this project include:

\begin{itemize}
	\item The software is capable of retrueving the Python SVN data to store within the database
	\item The user can log in to the system and view relevant data relating to their profile
	\item The user can view visualisations of bug reports and mail logs from the data stored in teh database
	\item The user can view statistics based on the data that is stored in the database
	\item A user (assuming they have permission) is able to manipulate the data stored in the database
\end{itemize}

A more in-depth look at project objectives can be found in section three.

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Deliverables}

The deliverables for this project consisted of these three core requirements:

\begin{itemize}
	\item Import Python Data
	\item Manipulate Python Data
	\item Visualise Python Data
\end{itemize}

From these requirements we were given a starting point to develop this advanced software along with documentation.

%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------

\section{Evolution of Software Development Plan}

This document has evolved from a detailed plan made in the early stages of development where we looked into the future of this project and set out to follow a set of activities in order to produce the highest quality product we could. Through following the initial plan we were able to come to this new updated Software Development Plan where we recount the actions that had taken place during the development process.

